`list`: store any type of objects in any dimensions unlike `c`.

```{r list, exercise = TRUE}

mylist <- list(
  "function" = function(x) {x + 1},
  "character" = letters[1:2],
  "integer" = 1L:2L,
  "matrix" = matrix(1:4, nrow = 2, byrow = T)
)

mylist
```

You can subset and use `list` in multiple ways.

```{r mylist, context='data',echo=F}

mylist <- list(
  "function" = function(x) {x + 1},
  "character" = letters[1:2],
  "integer" = 1L:2L,
  "matrix" = matrix(1:4, nrow = 2, byrow = T)
)

```

```{r list2, exercise = TRUE}
#--- subset by position ---#
mylist[[1]]

#--- subset by name ---#
mylist[c("function","integer")]


#--- call "function" by name and pass an input to the function ---#
mylist[["function"]](100) 


#--- call "matrix" by position and extract (2,2) element in the matrix ---#
mylist[[4]][2,2] 
```


`expand.grid`: Construct all possible combinations
```{r, context='data', echo=F}
param <- expand.grid(x = 1:2, 
                     y = letters[1:2])

```


```{r param, exercise=T}
param <- expand.grid(x = 1:2, 
                     y = letters[1:2])
param
```


`map`: Apply a list of inputs (one dimension) to a function
```{r map, exercise=T}
add_one <- function(input){input+1}
map(param$x, add_one)
```

Note that it returns output as a list. You can specify the type of output.

```{r map2, exercise=T}
add_one <- function(input){input+1}
map_chr(param$x, add_one)
```


`pmap`: Apply a list of inputs (multiple dimensions) to a function

```{r pmap, exercise=T}
bind <- function(input1,input2){paste0(input1,input2)}
pmap(list(param$x,param$y), bind)
```


You can return multiple outputs in each iteration and combine the results in a data frame.

```{r pmap2, exercise=T}
bind <- function(input1, input2) {
  list(
    output1 = paste0(input1, input2),
    output2 = paste0(input2, input1)
  )
}

pmap(list(param$x, param$y), bind) %>%
  bind_rows()
```

If the names of inputs and functions are identical, you can simplify your code. 

```{r pmap3, exercise=T}

bind <- function(x, y) {
  list(
    output1 = paste0(x, x),
    output2 = paste0(y, x)
  )
}

pmap(param, bind) %>%
  bind_rows()


```