We will generate data of the form:
$$y_{i}=\beta_{1}x_{1i}+\beta_{2}x_{2i} +\epsilon_{i},$$ where $x_{2i}=\gamma x_{1i}+\eta_{i}$, $x_{1i} \sim N(0,1)$ and $\eta_{i} \sim N(\sqrt{1-{\gamma}^2},1)$ for $i\in\{1,2,...,100\}$. 

For each simulation, we will estimate $\alpha_1$ from 
$$y_{i}=\alpha_{1}x_{1i} +e_{i},$$

We will consider all the following possible combinations of DGP:

-  $\epsilon_{i}: N(0,1)$ and student-$t$ distribution with $df=5$,
-  $\gamma \in\{0,.5,1\}$,
-  $\beta_{2} \in\{0,.5,1\}$

For each combination of DGP (2 x 3 x 3 = 12), we will do 200 simulations.




```{r coding, context='data', include=F}
library(tidyverse)
library(purrr)

#--- set seed ---#
set.seed(2021) 

#--- number of repetitions ---# 
num_reps <- 200

#--- sim func ---#
sim_func <- function(rep, n, gamma, b1, b2, dist_sim) {
  #--- DGP ---#
  df <- tibble(
    x1 = rnorm(n = n, 0, 1),
    x2 = gamma * x1 +  rnorm(n = n, sqrt(1 - gamma^2), 1),
    err = dist_list[[dist_sim]](n),
    Y = b1 * x1 + b2 * x2 + err
  )
  #--- estimate ---#
  reg <- lm(Y ~ 0+x1, data = df) # ignore intercept
  
  #--- store results of interest (potentially many) ---#
  results <- list(alpha = coefficients(reg)[1]) # put results in a list
  return(results)
}

#--- param list ---#
param_list <- expand.grid(
  rep = 1:num_reps,
  n = 100, 
  gamma = c(0, 0.5, 1),
  b1 = 1, 
  b2 = c(0, 0.5, 1), 
  dist_sim = c("Normal", "Student_t")
)

#--- dist list ---#
dist_list <- list(
  Normal = function(n) rnorm(n, 0, 1),
  Student_t = function(n) rt(n, 5)
)

#--- loop ---#
sim_out <-
  param_list %>%
  mutate(results = pmap(param_list, sim_func)) %>%
  unnest_wider(results) %>%  # this is useful if we stored multiple outputs
  group_by(gamma, b2) %>%
  mutate(mean_alpha = mean(alpha))

```



Let's start by setting things up.

```{r coding-setup, exercise=T}
#--- load packages ---#
library(tidyverse)
library(purrr)

#--- set seed ---#
set.seed(2021) 

#--- number of repetitions ---# 
num_reps <- 200
```



We first create a function that 1) randomly draw $n$ samples from DGP and 2) estimate $\alpha_1$. 

```{r coding-sim_func, exercise=T}
sim_func <- function(rep, n, gamma, b1, b2, dist_sim) {
  #--- DGP ---#
  df <- tibble(
    x1 = rnorm(n = n, 0, 1),
    x2 = gamma * x1 + sqrt(1 - gamma^2) * rnorm(n = n, 0, 1),
    err = dist_list[[dist_sim]](n),
    Y = b1 * x1 + b2 * x2 + err
  )
  
  #--- estimate alpha ---#
  reg <- lm(Y ~ 0+x1, data = df) # ignore intercept
  
  #--- store results of interest (potentially many) ---#
  results <- list(alpha = coefficients(reg)[1]) # put results in a list
  return(results)
}

```

We then specify all possible combinations of parameters. 
```{r param_list, exercise=T}
param_list <- expand.grid(
  rep = 1:num_reps,
  n = 100, 
  gamma = c(0, 0.5, 0.9),
  b1 = 1, 
  b2 = c(0, 0.5, 1), 
  dist_sim = c("Normal", "Student_t")
)

dim(param_list)
```


We then specify what `Normal` and `Student_t` means. 
```{r dist_list, exercise=T}
dist_list <- list(
  Normal = function(n) rnorm(n, 0, 1),
  Student_t = function(n) rt(n, 5)
)
```


Before we generalize, let's run a few.
```{r sample, exercise=T}
param_123 <- param_list[1:3,]
pmap(param_123, sim_func) %>%
  bind_rows()


```

It looks good. Now, let's combine our parameters and results.

```{r sim_out, exercise=T}
sim_out <-
  param_list %>%
  mutate(results = pmap(param_list, sim_func)) %>%
  unnest_wider(results) %>%  # this is useful if we stored multiple outputs
  group_by(gamma, b2) %>%
  mutate(mean_alpha = mean(alpha))

sim_out %>% head()
```

